Using temperature distributions of active regions to investigate flare activity

### 2014-12-09 paper.tex
More minor changes

%===========================================================================
\section{Discussion}
Figures 1 and 2 show that there is no clear trend in the long-term temperature distribution before flares occur.
This is also the case for the other active regions investigated. If any trend in temperature does occur before large flares, it may be on a shorter timescale than investigated here, and may only be noticable for very large flares.
Any further work on this topic should therefore look at shorter timespans with higher cadence, and perhaps only consider active regions associated with X-class flares.
From figure 3 it can be seen that there does appear to be some grouping of flaring active regions into groups of temperatures, and that a few of the larger flares are associated with active regions at higher temperatures than most of the other flares investigated.
However, no clear correlation can be seen between peak flare flux and active region temperature.
A much larger sample of flares is needed in order to properly determine whether or not a link exists between the two.

>>>>

%===========================================================================
\section{Discussion}

\subsubsection{Long-term temperature distribution}
Figures 1 and 2 show that there is no clear trend in the long-term temperature distribution before flares occur.
This is also the case for the other active regions investigated. If any trend in temperature does occur before large flares, it may be on a shorter timescale than investigated here, and may only be noticable for very large flares.
Any further work on this topic should therefore look at shorter timespans with higher cadence, and perhaps only consider active regions associated with X-class flares.

\subsubsection{Temperatures of active regions before flares}
From figure 3 it can be seen that there does appear to be some grouping of flaring active regions into groups of temperatures, and that a few of the larger flares are associated with active regions at higher temperatures than most of the other flares investigated.
However, no clear correlation can be seen between peak flare flux and active region temperature.
A much larger sample of flares is needed in order to properly determine whether or not a link exists between the two.
